---
title: "10x_5_15 Cell Cycle States"
output: html_notebook
---

This notebook produces a heatmap of the cell cycle states for each experiment in the 
10x_5_15 aggregate collection. The original source of all 28k cells is 
`/mnt/oncogxA/Projects/CPTRES/RNAExpression/10x/aggregates/10x_5_15/outs/filtered_gene_bc_matrices_mex/GRCh38`. 

I will first try to use all 28k cells but memory constraints may force me down to a 500 cell subset.

**Load Libraries**

```{r results="hide"}
library(grid)
library(plyr)
library(dplyr)
library(GSA)
library(liger)
library(matrixStats)
library(parallel)
library(pheatmap)
library(Seurat)
library(stringr)
library(reshape2)
```

# Load Single Cell Data Into Seurat

```{r}
scdata <- Read10X(data.dir="../subset_500/")
sc <- CreateSeuratObject(raw.data=scdata, min.cells=3, min.genes=3, project="10X_CPTRES")
```

# Seurat Preprocessing: Normalizing and Scaling

```{r results="hide"}
sc <- NormalizeData(object=sc, normalization.method="LogNormalize", scale.factor=10000)
sc <- ScaleData(object=sc)
```

# Cell Cycle Scoring
```{r results="hide"}
cc.genes <- readLines(con="../satija_cell_cycle/regev_lab_cell_cycle_genes.txt")
s.genes <- cc.genes[1:43]
g2m.genes <- cc.genes[44:97]
sc <- CellCycleScoring(object=sc, s.genes=s.genes, g2m.genes=g2m.genes, set.ident=T)
```

# Compile Experiment And Cell Phase

```{r}
exp.names <- c("r06_5", "r18_5", "s02", "s03", "r14_5", "r06_15",
               "r16_15", "r14_15", "r16_5", "caov3", "r18_15", "parent")
names(exp.names) <- 1:12
get.pop.name <- function(bc) {
  exp.names[as.numeric(strsplit(bc, "-")[[1]][2])]
}
cells.phases <- data.frame(
  phase = sc@meta.data$Phase,
  experiment = sapply(sc@cell.names, get.pop.name),
  stringsAsFactors=F
)
rownames(cells.phases) <- sc@cell.names
```

# Convert `cells.phases` Into A Phase x Experiment Matrix

```{r}
phase.count <- ddply(cells.phases, .(cells.phases$phase, cells.phases$experiment), nrow)
names(phase.count) <- c("phase", "experiment", "count")
phase.count.mat <- acast(phase.count, phase~experiment, value.var="count")
phase.count.mat <- phase.count.mat/colSums(phase.count.mat)[col(phase.count.mat)]
```

# Build Heatmap Of Normalized Matrix

```{r}
ph.500 <- pheatmap(phase.count.mat, cluster_rows=F, cluster_cols=T, 
                   show_rowname=T, show_colnames=T, silent=T)
```

# Plot Heatmap

```{r}
plot(ph.500$gtable)
```

# Redo Analysis Above w/28K Cells

```{r results="hide"}
scdata <- Read10X(data.dir="../full_28k/raw28k/")
sc <- CreateSeuratObject(raw.data=scdata, min.cells=3, min.genes=3, project="10X_CPTRES")
sc <- NormalizeData(object=sc, normalization.method="LogNormalize", scale.factor=10000)
sc <- ScaleData(object=sc)
cc.genes <- readLines(con="../satija_cell_cycle/regev_lab_cell_cycle_genes.txt")
s.genes <- cc.genes[1:43]
g2m.genes <- cc.genes[44:97]
sc <- CellCycleScoring(object=sc, s.genes=s.genes, g2m.genes=g2m.genes, set.ident=T)
exp.names <- c("r06_5", "r18_5", "s02", "s03", "r14_5", "r06_15",
               "r16_15", "r14_15", "r16_5", "caov3", "r18_15", "parent")
names(exp.names) <- 1:12
get.pop.name <- function(bc) {
  exp.names[as.numeric(strsplit(bc, "-")[[1]][2])]
}
cells.phases <- data.frame(
  phase = sc@meta.data$Phase,
  experiment = sapply(sc@cell.names, get.pop.name),
  stringsAsFactors=F
)
rownames(cells.phases) <- sc@cell.names
phase.count <- ddply(cells.phases, .(cells.phases$phase, cells.phases$experiment), nrow)
names(phase.count) <- c("phase", "experiment", "count")
phase.count.mat <- acast(phase.count, phase~experiment, value.var="count")
phase.count.mat <- phase.count.mat/colSums(phase.count.mat)[col(phase.count.mat)]
ph.28k <- pheatmap(phase.count.mat, cluster_rows=F, cluster_cols=T, 
                   show_rowname=T, show_colnames=T, silent=T)
```
```{r}
plot(ph.28k$gtable)
```


