---
title: "10x_c14agg Correlation/Clustering"
output: html_notebook
---

This notebook uses 3 random 500 cell subsets to calculate cell-cell correlation matrices.

This script used to generate random subsets of a `10X` matrix/barcodes/genes dataset is
[`subset_10x.R`](https://github.com/alex-wenzel/cptres-r/blob/master/subset_10x.R)

### Libraries

```{r results="hide"}
library(grid)
library(plyr)
library(dplyr)
library(GSA)
library(liger)
library(matrixStats)
library(parallel)
library(pheatmap)
library(Seurat)
library(stringr)
library(reshape2)
library(fgsea)
```

### Seurat Loading Function

Function to load, normalize, scale, and regress an input matrix by
cell cycle regression signal

```{r}
load.seurat <- function(spath) {
  scdata <- Read10X(data.dir=spath)
  sc <- CreateSeuratObject(raw.data=scdata, min.cells=3, min.genes=3, project="deep_5uM")
  sc <- NormalizeData(object=sc, normalization.method="LogNormalize", scale.factor=10000)
  sc <- ScaleData(object=sc)
  cc.genes <- readLines(con="../satija_cell_cycle/regev_lab_cell_cycle_genes.txt")
  s.genes <- cc.genes[1:43]
  g2m.genes <- cc.genes[44:97]
  sc <- CellCycleScoring(object=sc, s.genes=s.genes, g2m.genes=g2m.genes, set.ident=T)
  sc <- ScaleData(object=sc, vars.to.regress=c("S.Score", "G2M.Score"))
  return(sc)
}
```

### Load `10x_c14agg` Subsets

```{r}
sc.1 <- load.seurat("../10x_c14agg/subset_500_1/")
sc.2 <- load.seurat("../10x_c14agg/subset_500_2/")
sc.3 <- load.seurat("../10x_c14agg/subset_500_3/")
```

### Experiment Assignment Function

```{r}
exp.names <- c("r14_10u", "s02", "r14_15u_E", "s03", "r14_5u",
               "r14_15u_L", "caov3", "parent")
names(exp.names) <- 1:8

get.pop.name <- function(bc) {
  exp.names[as.numeric(strsplit(bc, "-")[[1]][2])]
}
```

### Get Experiment Names

```{r}
exps.1 <- sapply(sc.1@cell.names, get.pop.name)
exps.2 <- sapply(sc.2@cell.names, get.pop.name)
exps.3 <- sapply(sc.3@cell.names, get.pop.name)
```

### Correlation Matrices

```{r}
corr.mat.1 <- cor(sc.1@scale.data, method="spearman")
corr.mat.2 <- cor(sc.2@scale.data, method="spearman")
corr.mat.3 <- cor(sc.3@scale.data, method="spearman")
```

### Correlation Heatmaps

```{r}
anno.col.1 <- data.frame(
  Experiment=factor(exps.1)
)
ph.1 <- pheatmap(corr.mat.1, cluster_rows=T, cluster_cols=T, 
                 show_colnames=F, show_rownames=F, silent=T,
                 annotation_col=anno.col.1, annotation_row=anno.col.1)

anno.col.2 <- data.frame(
  Experiment=factor(exps.2)
)
ph.2 <- pheatmap(corr.mat.2, cluster_rows=T, cluster_cols=T,
                 show_colnames=F, show_rownames=F, silent=T,
                 annotation_col=anno.col.2, annotation_row=anno.col.2)

anno.col.3 <- data.frame(
  Experiment=factor(exps.3)
)
ph.3 <- pheatmap(corr.mat.3, cluster_rows=T, cluster_cols=T,
                 show_colnames=F, show_rownames=F, silent=T,
                 annotation_col=anno.col.3, annotation_row=anno.col.3)
```

```{r fig.height=8, fig.width=8}
plot(ph.1$gtable)
```

```{r fig.height=8, fig.width=8}
plot(ph.2$gtable)
```

```{r fig.height=8, fig.width=8}
plot(ph.3$gtable)
```

There is high variability between each of the three random cell samples in terms of
cell-cell correlation. Identify the variable genes in each matrix, reduce each of the matrices
to only contain those rows, and recalculate cell-cell correlation.

### Find Variables Genes

Use `Seurat::FindVariableGenes` to annotate each each subset.

```{r results="hide"}
sc.1 <- FindVariableGenes(object=sc.1, mean.function=ExpMean, dispersion.function=LogVMR,
                          x.low.cutoff=0.5, x.high.cutoff=3, y.cutoff=0.5, sort.results=T,
                          do.plot=F, display.progress=F)

sc.2 <- FindVariableGenes(object=sc.2, mean.function=ExpMean, dispersion.function=LogVMR,
                          x.low.cutoff=0.5, x.high.cutoff=3, y.cutoff=0.5, sort.results=T,
                          do.plot=F, display.progress=F)

sc.3 <- FindVariableGenes(object=sc.3, mean.function=ExpMean, dispersion.function=LogVMR,
                          x.low.cutoff=0.5, x.high.cutoff=3, y.cutoff=0.5, sort.results=T,
                          do.plot=F, display.progress=F)
```

### Filter For Variable Genes

Filter each `scale.data` to only contain its respective most variable genes

```{r}
var.sc1.scale.data <- sc.1@scale.data[sc.1@var.genes,]
var.sc2.scale.data <- sc.2@scale.data[sc.2@var.genes,]
var.sc3.scale.data <- sc.3@scale.data[sc.3@var.genes,]
```

### Variable Genes Correlation Matrices

```{r}
var.corr.mat.1 <- cor(var.sc1.scale.data, method="spearman")
var.corr.mat.2 <- cor(var.sc2.scale.data, method="spearman")
var.corr.mat.3 <- cor(var.sc3.scale.data, method="spearman")
```

### Get Experiment Names

```{r}
var.exps.1 <- sapply(colnames(var.sc1.scale.data), get.pop.name)
var.exps.2 <- sapply(colnames(var.sc2.scale.data), get.pop.name)
var.exps.3 <- sapply(colnames(var.sc3.scale.data), get.pop.name)
```

### Correlation Heatmaps

```{r}
var.anno.col.1 <- data.frame(
  Experiment=factor(var.exps.1)
)
var.ph.1 <- pheatmap(var.corr.mat.1, cluster_rows=T, cluster_cols=T, 
                 show_colnames=F, show_rownames=F, silent=T,
                 annotation_col=var.anno.col.1, annotation_row=var.anno.col.1)

var.anno.col.2 <- data.frame(
  Experiment=factor(var.exps.2)
)
var.ph.2 <- pheatmap(var.corr.mat.2, cluster_rows=T, cluster_cols=T,
                 show_colnames=F, show_rownames=F, silent=T,
                 annotation_col=var.anno.col.2, annotation_row=var.anno.col.2)

var.anno.col.3 <- data.frame(
  Experiment=factor(var.exps.3)
)
var.ph.3 <- pheatmap(var.corr.mat.3, cluster_rows=T, cluster_cols=T,
                 show_colnames=F, show_rownames=F, silent=T,
                 annotation_col=var.anno.col.3, annotation_row=var.anno.col.3)
```

```{r fig.height=8, fig.width=8}
plot(var.ph.1$gtable)
```

```{r fig.height=8, fig.width=8}
plot(var.ph.2$gtable)
```

```{r fig.height=8, fig.width=8}
plot(var.ph.3$gtable)
```

### Cutree Clustering For `sc.2`

```{r}
var.anno.col.2 <- data.frame(
  Experiment=factor(var.exps.2)
)
var.ph.2.cut <- pheatmap(var.corr.mat.2, cluster_rows=T, cluster_cols=T,
                 show_colnames=F, show_rownames=F, silent=T,
                 annotation_col=var.anno.col.2, annotation_row=var.anno.col.2,
                 cutree_cols=5)
```

```{r fig.height=8, fig.width=8}
plot(var.ph.2.cut$gtable)
```

### Extract Clusters

Get the clusters from the `sc.3` clustering and assign them as the identity for `sc.3`

```{r}
sc.2.ph.clust <- as.factor(cutree(var.ph.2.cut$tree_col, k=5))
attributes(sc.2.ph.clust)$names <- sc.2@cell.names
sc.2@ident <- sc.2.ph.clust
```

### Compile Experiment And Cluster

Build a dataframe of experiment and cluster and build a heatmap
showing the proportions of experiments in each cluster.

```{r}
sc.2.exps.clusters <- data.frame(
  experiment=sapply(sc.2@cell.names, get.pop.name),
  cluster=sc.2@ident,
  stringsAsFactors = F
)
rownames(sc.2.exps.clusters) <- sc.2@cell.names

sc.2.clust.count <- ddply(sc.2.exps.clusters, .(sc.2.exps.clusters$cluster, sc.2.exps.clusters$experiment), nrow)
names(sc.2.clust.count) <- c("cluster", "experiment", "count")
sc.2.clust.count.mat <- acast(sc.2.clust.count, cluster~experiment, value.var="count", fill=0)
sc.2.clust.count.mat <- sc.2.clust.count.mat/colSums(sc.2.clust.count.mat)[col(sc.2.clust.count.mat)]
```

```{r}
sc.2.clust.exp.hm <- pheatmap(sc.2.clust.count.mat, cluster_rows=F, cluster_cols=T,
                              show_rownames=T, show_colnames=T, silent=T)
```

```{r}
plot(sc.2.clust.exp.hm$gtable)
```