---
title: "10x_5_15 Original Clustering"
output: html_notebook
---

This notebook builds a heatmap representing the proportions of cells that are in each of the original
manuscript clusters. Heatmaps are built for the random 500 cell subset and the full 28k cells. Full 28k cells
are located at 
`/mnt/oncogxA/Projects/CPTRES/RNAExpression/10x/aggregates/10x_5_15/outs/filtered_gene_bc_matrices_mex/GRCh38`.


# **Load Libraries**

```{r results="hide"}
library(grid)
library(plyr)
library(dplyr)
library(GSA)
library(liger)
library(matrixStats)
library(parallel)
library(pheatmap)
library(Seurat)
library(stringr)
library(reshape2)
```

# Load Single Cell Data Into Seurat

```{r}
scdata <- Read10X(data.dir="../subset_500/")
sc <- CreateSeuratObject(raw.data=scdata, min.cells=3, min.genes=3, project="10X_CPTRES")
```

# Seurat Preprocessing: Normalizing and Scaling

```{r results="hide"}
sc <- NormalizeData(object=sc, normalization.method="LogNormalize", scale.factor=10000)
sc <- ScaleData(object=sc)
```

# Function Mapping Barcode To Experiment

```{r}
exp.names <- c("r06_5", "r18_5", "s02", "s03", "r14_5", "r06_15",
               "r16_15", "r14_15", "r16_5", "caov3", "r18_15", "parent")
names(exp.names) <- 1:12
get.pop.name <- function(bc) {
  exp.names[as.numeric(strsplit(bc, "-")[[1]][2])]
}
```

# Function Mapping Cluster Number To Collapsed Cluster Name

```{r}
cluster.names <- c("Large", "Small-1", "Medium-1", "Large", "Small-3",
                   "Large", "Medium-1", "Medium-2", "Small-2", "Medium-2",
                   "Small-4", "Medium-1", "Small-2", "Medium-2")
names(cluster.names) <- 1:14
get.cluster.name <- function(num) {
  cluster.names[num]
}
```

# Load Original 14 Clusters And Subset

```{r}
full.14.clusters <- read.csv("../full_28k/orig_graphclust_14/clusters.csv")
short.14.clusters <- full.14.clusters[which(full.14.clusters$Barcode %in% sc@cell.names),]
```

# Compile Experiment And Cluster

```{r}
exps.clusters <- data.frame(
  experiment = sapply(sc@cell.names, get.pop.name),
  cluster = sapply(short.14.clusters$Cluster, get.cluster.name),
  stringsAsFactors=F
)
rownames(exps.clusters) <- sc@cell.names
```

# Convert To Matrix

```{r}
clust.count <- ddply(exps.clusters, .(exps.clusters$cluster, exps.clusters$experiment), nrow)
names(clust.count) <- c("cluster", "experiment", "count")
clust.count.mat <- acast(clust.count, cluster~experiment, value.var="count", fill=0)
clust.count.mat <- clust.count.mat/colSums(clust.count.mat)[col(clust.count.mat)]
```

# Build Heatmap Of Normalized Matrix

```{r}
ph.500 <- pheatmap(clust.count.mat, cluster_rows=F, cluster_cols=F, 
                   show_rowname=T, show_colnames=T, silent=T)
```

# Plot Heatmap

```{r}
plot(ph.500$gtable)
```

# Redo Analysis Above w/28K Cells

```{r results="hide"}
scdata <- Read10X(data.dir="../full_28k/raw28k/")
sc <- CreateSeuratObject(raw.data=scdata, min.cells=3, min.genes=3, project="10X_CPTRES")
sc <- NormalizeData(object=sc, normalization.method="LogNormalize", scale.factor=10000)
sc <- ScaleData(object=sc)
exp.names <- c("r06_5", "r18_5", "s02", "s03", "r14_5", "r06_15",
               "r16_15", "r14_15", "r16_5", "caov3", "r18_15", "parent")
get.pop.name <- function(bc) {
  exp.names[as.numeric(strsplit(bc, "-")[[1]][2])]
}
cluster.names <- c("Large", "Small-1", "Medium-1", "Large", "Small-3",
                   "Large", "Medium-1", "Medium-2", "Small-2", "Medium-2",
                   "Small-4", "Medium-1", "Small-2", "Medium-2")
names(cluster.names) <- 1:14
get.cluster.name <- function(num) {
  cluster.names[num]
}
full.14.clusters <- read.csv("../full_28k/orig_graphclust_14/clusters.csv")
exps.clusters <- data.frame(
  experiment = sapply(sc@cell.names, get.pop.name),
  cluster = sapply(full.14.clusters$Cluster, get.cluster.name),
  stringsAsFactors=F
)
rownames(exps.clusters) <- sc@cell.names
clust.count <- ddply(exps.clusters, .(exps.clusters$cluster, exps.clusters$experiment), nrow)
names(clust.count) <- c("cluster", "experiment", "count")
clust.count.mat <- acast(clust.count, cluster~experiment, value.var="count", fill=0)
clust.count.mat <- clust.count.mat/colSums(clust.count.mat)[col(clust.count.mat)]
ph.28k <- pheatmap(clust.count.mat, cluster_rows=F, cluster_cols=T, 
                   show_rowname=T, show_colnames=T, silent=T)
```

```{r}
plot(ph.28k$gtable)
```

