---
title: "c14_agg Seurat Clusters With Cell Cycle"
output: html_notebook
---

This notebook builds a heatmap representing proportions of cells in each experiment
that are in each `Seurat` cluster built with PCA. Heatmaps are generated
first for a random 500 cell subset and this analysis is copied and condensed
into the last two cells for the full dataset.

### Load Libraries

```{r results="hide"}
library(grid)
library(plyr)
library(dplyr)
library(GSA)
library(liger)
library(matrixStats)
library(parallel)
library(pheatmap)
library(Seurat)
library(stringr)
library(reshape2)
```

### Load Single Cell Data, Scale And Normalize

```{r results="hide"}
scdata <- Read10X(data.dir="../10x_c14agg_500/")
sc <- CreateSeuratObject(raw.data=scdata, min.cells=3, min.genes=3, project="10X_CPTRES")
sc <- NormalizeData(object=sc, normalization.method="LogNormalize", scale.factor=10000)
sc <- ScaleData(object=sc)
```

### Cell Cycle Scoring And Regression

```{r results="hide"}
cc.genes <- readLines(con="../satija_cell_cycle/regev_lab_cell_cycle_genes.txt")
s.genes <- cc.genes[1:43]
g2m.genes <- cc.genes[44:97]
sc <- CellCycleScoring(object=sc, s.genes=s.genes, g2m.genes=g2m.genes, set.ident=T)
sc <- ScaleData(object=sc, vars.to.regress=c("S.Score", "G2M.Score"))
```

### Find Seurat Variable Genes and Run PCA

```{r results="hide"}
sc <- FindVariableGenes(object=sc, mean.function=ExpMean, 
                        dispersion.function=LogVMR, x.low.cutoff=0.0125,
                        x.high.cutoff=3, y.cutoff=0.5)
sc <- RunPCA(object=sc, pc.genes=sc@var.genes, do.print=F)
sc <- FindClusters(object=sc, reduction.type="pca", dims.use=1:10,
                   resolution=0.6, print.output=0, save.SNN=T)
```

### Function Mapping Barcode To Experiment

```{r}
exp.names <- c("r14_10u", "s02", "r14_15u_E", "s03", "r14_5u",
               "r14_15u_L", "caov3", "parent")
names(exp.names) <- 1:8
get.pop.name <- function(bc) {
  exp.names[as.numeric(strsplit(bc, "-")[[1]][2])]
}
```

### Compile Experiment And Cluster

```{r}
exps.clusters <- data.frame(
  experiment = sapply(sc@cell.names, get.pop.name),
  cluster = sc@ident,
  stringsAsFactors = F
)
```

### Convert To Matrix

```{r}
clust.count <- ddply(exps.clusters, .(exps.clusters$cluster, exps.clusters$experiment), nrow)
names(clust.count) <- c("cluster", "experiment", "count")
clust.count.mat <- acast(clust.count, cluster~experiment, value.var="count", fill=0)
clust.count.mat <- clust.count.mat/colSums(clust.count.mat)[col(clust.count.mat)]
```

### Build Heatmap Of Normalized Matrix

```{r}
ph.500 <- pheatmap(clust.count.mat, cluster_rows=F, cluster_cols=T, 
                   show_rowname=T, show_colnames=T, silent=T)
```

### Plot Heatmap

```{r}
plot(ph.500$gtable)
```

```{r results="hide"}
scdata <- Read10X(data.dir="../10x_c14agg/")
sc <- CreateSeuratObject(raw.data=scdata, min.cells=3, min.genes=3, project="10X_CPTRES")
sc <- NormalizeData(object=sc, normalization.method="LogNormalize", scale.factor=10000)
sc <- ScaleData(object=sc)
cc.genes <- readLines(con="../satija_cell_cycle/regev_lab_cell_cycle_genes.txt")
s.genes <- cc.genes[1:43]
g2m.genes <- cc.genes[44:97]
sc <- CellCycleScoring(object=sc, s.genes=s.genes, g2m.genes=g2m.genes, set.ident=T)
sc <- ScaleData(object=sc, vars.to.regress=c("S.Score", "G2M.Score"))
sc <- FindVariableGenes(object=sc, mean.function=ExpMean, 
                        dispersion.function=LogVMR, x.low.cutoff=0.0125,
                        x.high.cutoff=3, y.cutoff=0.5)
sc <- RunPCA(object=sc, pc.genes=sc@var.genes, do.print=F)
sc <- FindClusters(object=sc, reduction.type="pca", dims.use=1:10,
                   resolution=0.6, print.output=0, save.SNN=T)
exp.names <- c("r14_10u", "s02", "r14_15u_E", "s03", "r14_5u",
               "r14_15u_L", "caov3", "parent")
names(exp.names) <- 1:8
get.pop.name <- function(bc) {
  exp.names[as.numeric(strsplit(bc, "-")[[1]][2])]
}
exps.clusters <- data.frame(
  experiment = sapply(sc@cell.names, get.pop.name),
  cluster = sc@ident,
  stringsAsFactors = F
)
clust.count <- ddply(exps.clusters, .(exps.clusters$cluster, exps.clusters$experiment), nrow)
names(clust.count) <- c("cluster", "experiment", "count")
clust.count.mat <- acast(clust.count, cluster~experiment, value.var="count", fill=0)
clust.count.mat <- clust.count.mat/colSums(clust.count.mat)[col(clust.count.mat)]
p.full <- pheatmap(clust.count.mat, cluster_rows=F, cluster_cols=T, 
                   show_rowname=T, show_colnames=T, silent=T)
```

```{r}
plot(p.full$gtable)
```