---
title: "10x_5_15 GSEA"
output: html_notebook
---

This notebook uses the `fgsea` package to perform GSEA on the original clustering using
the [Hallmarks](http://software.broadinstitute.org/gsea/msigdb/download_file.jsp?filePath=/resources/msigdb/6.1/h.all.v6.1.symbols.gmt) and [Reactome](http://software.broadinstitute.org/gsea/msigdb/download_file.jsp?filePath=/resources/msigdb/6.1/c2.cp.reactome.v6.1.symbols.gmt) gene sets

### Load Libraries

```{r results="hide"}
library(grid)
library(plyr)
library(dplyr)
library(GSA)
library(liger)
library(matrixStats)
library(parallel)
library(pheatmap)
library(Seurat)
library(stringr)
library(reshape2)
library(fgsea)
```

### Preprocess With Seurat

Build a `Seurat` object, normalize, scale, regress cell cycle signal

```{r results="hide"}
scdata <- Read10X(data.dir="../full_28k/raw28k/")
sc <- CreateSeuratObject(raw.data=scdata, min.cells=3, min.genes=3, project="10X_CPTRES")
sc <- NormalizeData(object=sc, normalization.method="LogNormalize", scale.factor=10000)
sc <- ScaleData(object=sc)
cc.genes <- readLines(con="../satija_cell_cycle/regev_lab_cell_cycle_genes.txt")
s.genes <- cc.genes[1:43]
g2m.genes <- cc.genes[44:97]
sc <- CellCycleScoring(object=sc, s.genes=s.genes, g2m.genes=g2m.genes, set.ident=T)
sc <- ScaleData(object=sc, vars.to.regress=c("S.Score", "G2M.Score"))
```

### Function Mapping Cluster Number To Collapsed Cluster Name

```{r}
cluster.names <- c("Large", "Small-1", "Medium-1", "Large", "Small-3",
                   "Large", "Medium-1", "Medium-2", "Small-2", "Medium-2",
                   "Small-4", "Medium-1", "Small-2", "Medium-2")
names(cluster.names) <- 1:14
get.cluster.name <- function(num) {
  cluster.names[num]
}
```

### Load Original Clusters

Load the original clusters and assign to `sc@ident`

```{r results="hide"}
full.14.clusters <- read.csv("../full_28k/orig_graphclust_14/clusters.csv")$Cluster
full.14.clusters <- as.factor(sapply(full.14.clusters, get.cluster.name))
attributes(full.14.clusters)$names <- sc@cell.names
sc@ident <- full.14.clusters
```

### Find Differentially Expressed Genes

The first cell below calls `Seurat::FindAllMarkers` and saves the resulting dataframe
to a `.tsv`. The second cell loads the file from the `.tsv`. Due to long running time,
only run the first cell if it hasn't yet been run or if the parameters or input data set
change.

```{r results="hide"}
sc.markers <- FindAllMarkers(object=sc, min.pct=0.25, thresh.use=0.25)
write.table(sc.markers, "../10x_5_15_gsea_markers.tsv", quote=FALSE, row.names=FALSE, sep='\t')
```

```{r results="hide"}
sc.markers <- read.csv("../10x_5_15_gsea_markers.tsv", sep='\t', stringsAsFactors = F)
```

### Heatmap Of Top 10 Genes In Each Cluster

```{r fig.height=11, fig.width=12}
top.10.genes <- sc.markers %>% group_by(cluster) %>% top_n(10, avg_logFC)
DoHeatmap(object=sc, genes.use=top.10.genes$gene, slim.col.label=T, remove.key=T)
```

### Load Gene Sets

```{r results="hide"}
hallmarks.full <- GSA.read.gmt("../msigdb/h.all.v6.1.symbols.gmt")
hallmarks <- hallmarks.full$genesets
names(hallmarks) <- hallmarks.full$geneset.names

reactome.full <- GSA.read.gmt("../msigdb/c2.cp.reactome.v6.1.symbols.gmt")
reactome <- reactome.full$genesets
names(reactome) <- reactome.full$geneset.names
```

### GSEA Wrapper

```{r}
run.fgsea <- function(cluster.name, gene.set) {
  cluster.markers <- sc.markers[sc.markers$cluster==cluster.name,]
  cluster.stats <- cluster.markers$avg_logFC
  names(cluster.stats) <- cluster.markers$gene
  res <- fgsea(pathways=gene.set, stats=cluster.stats, nperm=10000, minSize=10)
  top.pathways.up <- res[ES>0,][head(order(pval), n=10), pathway]
  top.pathways.dn <- res[ES<0,][head(order(pval), n=10), pathway]
  top.pathways <- c(top.pathways.up, rev(top.pathways.dn))
  plotGseaTable(gene.set[top.pathways], cluster.stats, res, gseaParam=0.5)
  return(res)
}
```


### Run GSEA For Each Cluster

```{r fig.width=20}
large.hmrks <- run.fgsea("Large", hallmarks)
large.react <- run.fgsea("Large", reactome)

medium1.hmrks <- run.fgsea("Medium-1", hallmarks)
medium1.react <- run.fgsea("Medium-1", reactome)

medium2.hmrks <- run.fgsea("Medium-2", hallmarks)
medium2.react <- run.fgsea("Medium-2", reactome)

small1.hmrks <- run.fgsea("Small-1", hallmarks)
small1.react <- run.fgsea("Small-1", reactome)

small2.hmrks <- run.fgsea("Small-2", hallmarks)
small2.react <- run.fgsea("Small-2", reactome)

small3.hmrks <- run.fgsea("Small-3", hallmarks)
small3.react <- run.fgsea("Small-3", reactome)

small4.hmrks <- run.fgsea("Small-4", hallmarks)
small4.react <- run.fgsea("Small-4", reactome)
```

