---
title: "10x_c14agg Analysis12"
output: html_notebook
---

Implements the analysis in `analysis12.R` adapted for the c14_agg cells.

**Load Libraries**

```{r results="hide"}
library(grid)
library(plyr)
library(dplyr)
library(GSA)
library(liger)
library(matrixStats)
library(parallel)
library(pheatmap)
library(Seurat)
library(stringr)
library(reshape2)
```

### Load, Scale, Normalize Seurat Data

```{r results="hide"}
scdata <- Read10X(data.dir="../10x_c14agg_500/")
sc <- CreateSeuratObject(raw.data=scdata, min.cells=3, min.genes=3, project="10X_CPTRES")
sc <- NormalizeData(object=sc, normalization.method="LogNormalize", scale.factor=10000)
sc <- ScaleData(object=sc)
```


### Load Cell Cycle Data

```{r}
cc.genes <- readLines(con="../satija_cell_cycle/regev_lab_cell_cycle_genes.txt")
s.genes <- cc.genes[1:43]
g2m.genes <- cc.genes[44:97]
```

### Cell Cycle Scoring and Regression

```{r results="hide"}
sc <- CellCycleScoring(object=sc, s.genes=s.genes, g2m.genes=g2m.genes, set.ident=T)
sc <- ScaleData(object=sc, vars.to.regress=c("S.Score", "G2M.Score"))
```

### Function Mapping Cluster To Experiment

```{r}
exp.names <- c("r14_10u", "s02", "r14_15u_E", "s03", "r14_5u",
               "r14_15u_L", "caov3", "parent")
names(exp.names) <- 1:8

get.pop.name <- function(bc) {
  exp.names[as.numeric(strsplit(bc, "-")[[1]][2])]
}
```

### Compile Barcode And Experiment Name

```{r}
barcode.src <- data.frame(sc@raw.data@Dimnames[[2]])
names(barcode.src) <- c("src")
barcode.src$src <- lapply(as.character(barcode.src$src), get.pop.name)
rownames(barcode.src) <- sc@raw.data@Dimnames[[2]]
```

### Convert Seurat Scaled Data To Matrix

```{r}
expr.mat <- as.matrix(sc@scale.data)
```

### Filter Matrix To Contain Rows With < 10 zeros

```{r}
n.zero.lim = 5
prevalent.genes <- as.matrix(sc@scale.data[rowSums(sc@data==0)<=n.zero.lim,])
```

### Run Seurat's PCA On `prevalent.genes` And Find Clusters

```{r}
sc <- RunPCA(object=sc, pc.genes=rownames(prevalent.genes), do.print=F)
sc <- FindClusters(object=sc, reduction.type="pca", dims.use=1:10,
                   resolution=0.6, print.output=0, save.SNN=T)
```

### Build Annotation Column For Heatmap

```{r}
anno.col <- data.frame(
  Experiment=factor(unlist(barcode.src$src)),
  Cell.Cycle=sc@meta.data$Phase,
  Seurat.Cluster=sc@ident
)
rownames(anno.col) <- colnames(prevalent.genes)
all.colors <- c(
  "#5e693e",
  "#8449c0",
  "#a0cd54",
  "#cc538e",
  "#92cbae",
  "#4e3049",
  "#c66a43",
  "#9396c3"
)
hm.anno.colors <- list(
  Experiment=all.colors,
  Cell.Cycle=all.colors[1:3],
  Seurat.Cluster=all.colors[1:5]
)
names(hm.anno.colors$Experiment) <- attr(anno.col$Experiment, "levels")
names(hm.anno.colors$Cell.Cycle) <- attr(anno.col$Cell.Cycle, "levels")
names(hm.anno.colors$Seurat.Cluster) <- attr(anno.col$Seurat.Cluster, "levels")
```

### Build Heatmap

```{r}
ph500 <- pheatmap(prevalent.genes, show_rownames=F, show_colnames=F, 
         cluster_rows=F, annotation_col=anno.col, silent=T,
         annotation_colors=hm.anno.colors)
```

```{r fig.height=6}
plot(ph500$gtable)
```




