---
title: "10x_c14agg Sample GSEA"
output: html_notebook
---

This notebook performs GSEA on the R14 clones without clustering - it groups them by sample of origin. This notebook
does ***not*** use cell cycle regression.

### Libraries

```{r results="hide"}
library(grid)
library(plyr)
library(dplyr)
library(GSA)
library(liger)
library(matrixStats)
library(parallel)
library(pheatmap)
library(Seurat)
library(stringr)
library(reshape2)
library(fgsea)
```

### Load Seurat

Again, *no cell cycle regression!!*

```{r}
scdata <- Read10X(data.dir="../10x_c14agg/")
sc <- CreateSeuratObject(raw.data=scdata, min.cells=3, min.genes=3, project="10x_c14agg")
sc <- NormalizeData(object=sc, normalization.method="LogNormalize", scale.factor=10000)
sc <- ScaleData(object=sc)
```

### Assign Sample Names

Assign the cell sample of origin to use in place of clustering results.

```{r}
exp.names <- c("r14_10u", "s02", "r14_15u_E", "s03", "r14_5u",
               "r14_15u_L", "caov3", "parent")
names(exp.names) <- 1:8

get.pop.name <- function(bc) {
  exp.names[as.numeric(strsplit(bc, "-")[[1]][2])]
}
sc@ident <- as.factor(sapply(sc@cell.names, get.pop.name))
attributes(sc@ident)$names <- sc@cell.names
```

### Load Gene Sets

```{r results="hide"}
hallmarks.full <- GSA.read.gmt("../msigdb/h.all.v6.1.symbols.gmt")
hallmarks <- hallmarks.full$genesets
names(hallmarks) <- hallmarks.full$geneset.names

reactome.full <- GSA.read.gmt("../msigdb/c2.cp.reactome.v6.1.symbols.gmt")
reactome <- reactome.full$genesets
names(reactome) <- reactome.full$geneset.names
```

### GSEA Wrapper

```{r}
run.fgsea <- function(cluster.name, gene.set, pcut, markers) {
  cluster.markers <- markers[markers$cluster==cluster.name,]
  cluster.stats <- cluster.markers$avg_logFC
  names(cluster.stats) <- cluster.markers$gene
  res <- fgsea(pathways=gene.set, stats=cluster.stats, nperm=10000, minSize=10)
  res <- res[res$padj<pcut,]
  res$cluster <- cluster.name
  return(res)
}
```

### Find DEG Markers

```{r}
sc.markers <- FindAllMarkers(object=sc, min.pct=0, thresh.use=0)
```

### Heatmap Of Top 10 Genes In Each Cluster

```{r fig.height=11, fig.width=12}
top.10.genes <- sc.markers %>% group_by(cluster) %>% top_n(10, avg_logFC)
DoHeatmap(object=sc, genes.use=top.10.genes$gene, slim.col.label=T, remove.key=T)
```

### Run GSEA

```{r}
hmrks <- run.fgsea("r14_10u", hallmarks, 0.05, sc.markers)

for (i in 2:length(exp.names)) {
  hmrks <- rbind(hmrks, run.fgsea(exp.names[i], hallmarks, 0.05, sc.markers))
}
```

### Matrix + Heatmap

```{r}
hmrks.mat <- acast(hmrks, pathway~cluster, value.var="NES", fill=0)
hmrks.hm <- pheatmap(hmrks.mat, silent=F, cluster_rows=F, cluster_cols=F,
                     fontsize=14, border_color="black")
```

