---
title: "10x_5_15 Step 5 vs Step 15 Differential Genes"
output: html_notebook
---

This notebook builds heatmaps of differentially expressed genes between each of the step5 cells and 
step15 cells within each of the four resistant clones.

### Libraries

```{r}
library(grid)
library(plyr)
library(dplyr)
library(GSA)
library(liger)
library(matrixStats)
library(parallel)
library(pheatmap)
library(Seurat)
library(stringr)
library(reshape2)
library(fgsea)
library(biomaRt)
```

### Load Seurat

Load data ***without*** applying cell cycle regression.

```{r}
scdata <- Read10X(data.dir="../full_28k/raw28k/")
sc <- CreateSeuratObject(raw.data=scdata, min.cells=3, min.genes=3, project="10x_5_15")
sc <- NormalizeData(object=sc, normalization.method="LogNormalize", scale.factor=10000)
sc <- ScaleData(object=sc)
```

### Assign Experiment Names

```{r}
exp.names <- c("r06_5", "r18_5", "s02", "s03", "r14_5", "r06_15",
               "r16_15", "r14_15", "r16_5", "caov3", "r18_15", "parent")
names(exp.names) <- 1:12

get.pop.name <- function(bc) {
  exp.names[as.numeric(strsplit(bc, "-")[[1]][2])]
}

sc@ident <- as.factor(sapply(sc@cell.names, get.pop.name))
names(sc@ident) <- sc@cell.names
```

### Differential Genes Between Steps For Each Clone

```{r}
markers.r06 <- FindMarkers(object=sc, ident.1="r06_5", ident.2="r06_15")
markers.r14 <- FindMarkers(object=sc, ident.1="r14_5", ident.2="r14_15")
markers.r16 <- FindMarkers(object=sc, ident.1="r16_5", ident.2="r16_15")
markers.r18 <- FindMarkers(object=sc, ident.1="r18_15", ident.2="r18_5")
```
### Sort Markers by Fold Change

```{r}
markers.r06 <- markers.r06[order(-markers.r06$avg_logFC),]
markers.r14 <- markers.r14[order(-markers.r14$avg_logFC),]
markers.r16 <- markers.r16[order(-markers.r16$avg_logFC),]
markers.r18 <- markers.r18[order(-markers.r18$avg_logFC),]
```

### Top Upregulated Genes

```{r}
r06.top.50 <- c(head(rownames(markers.r06), 25), tail(rownames(markers.r06), 25))
r14.top.50 <- c(head(rownames(markers.r14), 25), tail(rownames(markers.r14), 25))
r16.top.50 <- c(head(rownames(markers.r16), 25), tail(rownames(markers.r16), 25))
r18.top.50 <- c(head(rownames(markers.r18), 25), tail(rownames(markers.r18), 25))
```

### Clone DEG Heatmaps

```{r fig.height=8}
DoHeatmap(object=sc, genes.use=r06.top.50, slim.col.label=T, remove.key=T,
          cells.use=sc@cell.names[sapply(sc@cell.names, get.pop.name) %in% c("r06_5", "r06_15")])
```

```{r fig.height=8}
DoHeatmap(object=sc, genes.use=r14.top.50, slim.col.label=T, remove.key=T,
          cells.use=sc@cell.names[sapply(sc@cell.names, get.pop.name) %in% c("r14_5", "r14_15")])
```

```{r fig.height=8}
DoHeatmap(object=sc, genes.use=r16.top.50, slim.col.label=T, remove.key=T,
          cells.use=sc@cell.names[sapply(sc@cell.names, get.pop.name) %in% c("r16_5", "r16_15")])
```

```{r fig.height=8}
DoHeatmap(object=sc, genes.use=r18.top.50, slim.col.label=T, remove.key=T,
          cells.use=sc@cell.names[sapply(sc@cell.names, get.pop.name) %in% c("r18_5", "r18_15")])
```

### Load Gene Sets

```{r}
hallmarks.full <- GSA.read.gmt("../msigdb/h.all.v6.1.symbols.gmt")
hallmarks <- hallmarks.full$genesets
names(hallmarks) <- hallmarks.full$geneset.names

reactome.full <- GSA.read.gmt("../msigdb/c2.cp.reactome.v6.1.symbols.gmt")
reactome <- reactome.full$genesets
names(reactome) <- reactome.full$geneset.names
```

### GSEA Wrapper

```{r}
run.fgsea <- function(gene.set, pcut, markers) {
  cluster.stats <- markers$avg_logFC
  names(cluster.stats) <- rownames(markers)
  res <- fgsea(pathways=gene.set, stats=cluster.stats, nperm=10000, minSize=10)
  res <- res[res$padj<pcut,]
  return(res)
}
```

### Clone GSEAs

```{r}
r06.hmrks <- run.fgsea(hallmarks, 0.05, markers.r06)
r06.react <- run.fgsea(reactome, 0.05, markers.r06)

r14.hmrks <- run.fgsea(hallmarks, 0.05, markers.r14)
r14.react <- run.fgsea(reactome, 0.05, markers.r14)

r16.hmrks <- run.fgsea(hallmarks, 0.05, markers.r16)
r16.react <- run.fgsea(reactome, 0.05, markers.r16)

r18.hmrks <- run.fgsea(hallmarks, 0.05, markers.r18)
r18.react <- run.fgsea(reactome, 0.05, markers.r18)
```

