---
title: "10x_5_15 GSEA Matrix"
output: html_notebook
---

This notebook produces a GSEA matrix using `fgsea` based on [`10x_c14agg_gsea`](https://github.com/alex-wenzel/cptres-r/blob/master/10x_c14agg_gsea.Rmd)

### Libraries

```{r results="hide"}
library(grid)
library(plyr)
library(dplyr)
library(GSA)
library(liger)
library(matrixStats)
library(parallel)
library(pheatmap)
library(Seurat)
library(stringr)
library(reshape2)
library(fgsea)
```

### Load Seurat

```{r}
scdata <- Read10X(data.dir="../full_28k/raw28k/")
sc <- CreateSeuratObject(raw.data=scdata, min.cells=3, min.genes=3, project="10x_5_15")
sc <- NormalizeData(object=sc, normalization.method="LogNormalize", scale.factor=10000)
sc <- ScaleData(object=sc)
cc.genes <- readLines(con="../satija_cell_cycle/regev_lab_cell_cycle_genes.txt")
s.genes <- cc.genes[1:43]
g2m.genes <- cc.genes[44:97]
sc <- CellCycleScoring(object=sc, s.genes=s.genes, g2m.genes=g2m.genes, set.ident=T)
sc <- ScaleData(object=sc, vars.to.regress=c("S.Score", "G2M.Score"))
```

### Find Seurat Variable Genes and Run PCA

```{r results="hide"}
sc <- FindVariableGenes(object=sc, mean.function=ExpMean, 
                        dispersion.function=LogVMR, x.low.cutoff=0.0125,
                        x.high.cutoff=3, y.cutoff=0.5, do.plot=F)
sc <- RunPCA(object=sc, pc.genes=sc@var.genes, do.print=F)
sc <- FindClusters(object=sc, reduction.type="pca", dims.use=1:10,
                   resolution=0.6, print.output=0, save.SNN=T)
```
### Compile Experiment and Seurat Cluster

This cell produces a heatmap to analyze the how Seurat clustering performs to separate
the experiments.

```{r}
exp.names <- c("r06_5", "r18_5", "s02", "s03", "r14_5", "r06_15",
               "r16_15", "r14_15", "r16_5", "caov3", "r18_15", "parent")
names(exp.names) <- 1:12

get.pop.name <- function(bc) {
  exp.names[as.numeric(strsplit(bc, "-")[[1]][2])]
}

exps.clusts <- data.frame(
  experiment=sapply(sc@cell.names, get.pop.name),
  cluster=as.character(sc@ident),
  stringsAsFactors=F
)
rownames(exps.clusts) <- sc@cell.names

clust.count <- ddply(exps.clusts, .(exps.clusts$cluster, exps.clusts$experiment), nrow)
names(clust.count) <- c("cluster", "experiment", "count")
clust.count.mat <- acast(clust.count, cluster~experiment, value.var="count", fill=0)
clust.count.mat <- clust.count.mat/colSums(clust.count.mat)[col(clust.count.mat)]

exps.clusts.hm <- pheatmap(clust.count.mat, cluster_rows=F, cluster_cols=T, 
                   show_rownames=T, show_colnames=T, silent=F,
                   fontsize=20, background_color="black")
```

### Load Gene Sets

```{r results="hide"}
hallmarks.full <- GSA.read.gmt("../msigdb/h.all.v6.1.symbols.gmt")
hallmarks <- hallmarks.full$genesets
names(hallmarks) <- hallmarks.full$geneset.names

reactome.full <- GSA.read.gmt("../msigdb/c2.cp.reactome.v6.1.symbols.gmt")
reactome <- reactome.full$genesets
names(reactome) <- reactome.full$geneset.names
```

### GSEA Wrapper

```{r}
run.fgsea <- function(cluster.name, gene.set, pcut, markers) {
  cluster.markers <- markers[markers$cluster==cluster.name,]
  cluster.stats <- cluster.markers$avg_logFC
  names(cluster.stats) <- cluster.markers$gene
  res <- fgsea(pathways=gene.set, stats=cluster.stats, nperm=10000, minSize=10)
  res <- res[res$padj<pcut,]
  res$cluster <- cluster.name
  return(res)
}
```

### Find DEG Markers

```{r}
sc.markers.tu0 <- FindAllMarkers(object=sc, min.pct=0, thresh.use=0)
```

### Run GSEA For Each Cluster

```{r fig.width=20}
hmrks.tu0 <- run.fgsea("0", hallmarks, 0.05, sc.markers.tu0)
react.tu0 <- run.fgsea("0", reactome, 0.05, sc.markers.tu0)

for (i in 1:8) {
  hmrks.tu0 <- rbind(hmrks.tu0, run.fgsea(as.character(i), hallmarks, 0.05, sc.markers.tu0))
}

for (i in 1:8) {
  react.tu0 <- rbind(react.tu0, run.fgsea(as.character(i), reactome, 0.05, sc.markers.tu0))
}
```

### Process Into Matrix for Heatmap

```{r}
hmrks.tu0.mat <- acast(hmrks.tu0, pathway~cluster, value.var="NES", fill=0)
hmrks.tu0.hm <- pheatmap(hmrks.tu0.mat, silent=F, cluster_rows=F, cluster_cols=F,
                     fontsize=14, border_color="black")
```

### Find DEG Markers

```{r}
sc.markers.tu25 <- FindAllMarkers(object=sc, min.pct=0, thresh.use=0.25)
```

### Run GSEA For Each Cluster

```{r fig.width=20}
hmrks.tu25 <- run.fgsea("0", hallmarks, 0.05, sc.markers.tu25)
react.tu25 <- run.fgsea("0", reactome, 0.05, sc.markers.tu25)

for (i in 1:8) {
  hmrks.tu25 <- rbind(hmrks.tu25, run.fgsea(as.character(i), hallmarks, 0.05, sc.markers.tu25))
}

for (i in 1:8) {
  react.tu25 <- rbind(react.tu25, run.fgsea(as.character(i), reactome, 0.05, sc.markers.tu25))
}
```

### Process Into Matrix for Heatmap

```{r}
hmrks.tu25.mat <- acast(hmrks.tu25, pathway~cluster, value.var="NES", fill=0)
hmrks.tu25.hm <- pheatmap(hmrks.tu25.mat, silent=F, cluster_rows=F, cluster_cols=F,
                     fontsize=14, border_color="black")
```