---
title: "Cell Cycle Cluster Comparison"
output: html_notebook
---

This notebook compares the effect of regressing the cell cycle signal on `Seurat` PCA clustering. Clusters are
generated for each of `10x_5_15`, `deep_5uM` and `10x_c14agg` and visualized on the basis of how experiment
populations divide into clusters.

### Libraries

### Libraries

```{r results="hide"}
library(grid)
library(plyr)
library(dplyr)
library(GSA)
library(liger)
library(matrixStats)
library(parallel)
library(pheatmap)
library(Seurat)
library(stringr)
library(reshape2)
library(fgsea)
```

### Clustering Function

This function takes the path to `10X` data and a flag indicating whether to perform cell cycle regression
and returns a `Seurat` object with clustering applied.

```{r}
get.pop.name <- function(bc) {
  exp.names[as.numeric(strsplit(bc, "-")[[1]][2])]
}

seurat.cluster <- function(path, do.ccr, exp.names) {
  scdata <- Read10X(data.dir=path)
  sc <- CreateSeuratObject(raw.data=scdata, min.cells=3, min.genes=3, project="10x_c14agg")
  sc <- NormalizeData(object=sc, normalization.method="LogNormalize", scale.factor=10000)
  sc <- ScaleData(object=sc)
  if (do.ccr) {
    cc.genes <- readLines(con="../satija_cell_cycle/regev_lab_cell_cycle_genes.txt")
    s.genes <- cc.genes[1:43]
    g2m.genes <- cc.genes[44:97]
    sc <- CellCycleScoring(object=sc, s.genes=s.genes, g2m.genes=g2m.genes, set.ident=T)
    sc <- ScaleData(object=sc, vars.to.regress=c("S.Score", "G2M.Score"))
  }
  sc <- FindVariableGenes(object=sc, mean.function=ExpMean, 
                        dispersion.function=LogVMR, x.low.cutoff=0.0125,
                        x.high.cutoff=3, y.cutoff=0.5, do.plot=F)
  sc <- RunPCA(object=sc, pc.genes=sc@var.genes, do.print=F)
  sc <- FindClusters(object=sc, reduction.type="pca", dims.use=1:10,
                    resolution=0.6, print.output=0, save.SNN=T)
  exps.clusts <- data.frame(
    experiment=sapply(sc@cell.names, get.pop.name),
    cluster=as.character(sc@ident),
    stringsAsFactors=F
  )
  rownames(exps.clusts) <- sc@cell.names
  
  clust.count <- ddply(exps.clusts, .(exps.clusts$cluster, exps.clusts$experiment), nrow)
  names(clust.count) <- c("cluster", "experiment", "count")
  clust.count.mat <- acast(clust.count, cluster~experiment, value.var="count", fill=0)
  clust.count.mat <- clust.count.mat/colSums(clust.count.mat)[col(clust.count.mat)]
  
  exps.clusts.hm <- pheatmap(clust.count.mat, cluster_rows=F, cluster_cols=F, 
                     show_rownames=T, show_colnames=T, silent=T)
  return(exps.clusts.hm)
}
```

### Clustering `10x_5_15` **WITH** Cell Cycle Regression

```{r}
exp.names <- c("r06_5", "r18_5", "s02", "s03", "r14_5", "r06_15",
               "r16_15", "r14_15", "r16_5", "caov3", "r18_15", "parent")
names(exp.names) <- 1:12 
hm.10x_5_15 <- seurat.cluster(path="../full_28k/raw28k/", do.ccr=T, exp.names=exp.names)
```

```{r}
plot(hm.10x_5_15$gtable)
```

### Clustering `10x_5_15` **WITHOUT** Cell Cycle Regression

```{r}
exp.names <- c("r06_5", "r18_5", "s02", "s03", "r14_5", "r06_15",
               "r16_15", "r14_15", "r16_5", "caov3", "r18_15", "parent")
names(exp.names) <- 1:12 
hm.10x_5_15 <- seurat.cluster(path="../full_28k/raw28k/", do.ccr=F, exp.names=exp.names)
```

```{r}
plot(hm.10x_5_15$gtable)
```

### Clustering `10x_c14agg` **WITH** Cell Cycle Regression

```{r}
exp.names <- c("r14_10u", "s02", "r14_15u_E", "s03", "r14_5u",
               "r14_15u_L", "caov3", "parent")
names(exp.names) <- 1:8
hm.10x_c14agg <- seurat.cluster(path="../10x_c14agg/", do.ccr=T, exp.names=exp.names)
```

```{r}
plot(hm.10x_c14agg$gtable)
```

### Clustering `10x_c14agg` **WITHOUT** Cell Cycle Regression

```{r}
exp.names <- c("r14_10u", "s02", "r14_15u_E", "s03", "r14_5u",
               "r14_15u_L", "caov3", "parent")
names(exp.names) <- 1:8
hm.10x_c14agg <- seurat.cluster(path="../10x_c14agg/", do.ccr=F, exp.names=exp.names)
```

```{r}
plot(hm.10x_c14agg$gtable)
```

### Clustering `deep_5uM` **WITH** Cell Cycle Regression

```{r}
exp.names <- c("S02", "S03", "caov3", "parent", "R06_5uM", "R14_5uM",                                                  
               "R16_5uM", "R18_5uM")                                                                                   
names(exp.names) <- 1:8
hm.deep_5um <- seurat.cluster(path="../deep_5uM/", do.ccr=T, exp.names=exp.names)
```

```{r}
plot(hm.deep_5um$gtable)
```

### Clustering `deep_5uM` **WITHOUT** Cell Cycle Regression

```{r}
exp.names <- c("S02", "S03", "caov3", "parent", "R06_5uM", "R14_5uM",                                                  
               "R16_5uM", "R18_5uM")                                                                                   
names(exp.names) <- 1:8
hm.deep_5um <- seurat.cluster(path="../deep_5uM/", do.ccr=F, exp.names=exp.names)
```

```{r}
plot(hm.deep_5um$gtable)
```
