---
title: "deep_5uM Cell Cycle Assignment"
output: html_notebook
---

This notebook assigns cell cycle phases to the deep sequencing experiment of the sensitive and
step 5 clones. The path to this data on oncogxA is

`/mnt/oncogxA/Projects/CPTRES/RNAExpression/10x/aggregates/deep_5uM`

This notebook builds cell cycle heatmaps for experiment ID, 10X graph-based clustering, 
and Seurat variable genes clustering.

### Libraries

```{r results="hide"}
library(grid)
library(plyr)
library(dplyr)
library(GSA)
library(liger)
library(matrixStats)
library(parallel)
library(pheatmap)
library(Seurat)
library(stringr)
library(reshape2)
library(fgsea)
```

### Load deep_5uM Data

Load the data with Seurat

```{r results="hide"}
scdata <- Read10X(data.dir="../deep_5uM/")
sc <- CreateSeuratObject(raw.data=scdata, min.cells=3, min.genes=3, project="deep_5uM")
sc <- NormalizeData(object=sc, normalization.method="LogNormalize", scale.factor=10000)
sc <- ScaleData(object=sc)
```

### Assign Cell Cycle Phases

```{r}
cc.genes <- readLines(con="../satija_cell_cycle/regev_lab_cell_cycle_genes.txt")
s.genes <- cc.genes[1:43]
g2m.genes <- cc.genes[44:97]
sc <- CellCycleScoring(object=sc, s.genes=s.genes, g2m.genes=g2m.genes, set.ident=T)
```

### Compile Cell Cycle And Experiment

```{r}
exp.names <- c("S02", "S03", "caov3", "parent", "R06_5uM", "R14_5uM",
               "R16_5uM", "R18_5uM")
names(exp.names) <- 1:8
get.pop.name <- function(bc) {
  exp.names[as.numeric(strsplit(bc, "-")[[1]][2])]
}
cells.phases <- data.frame(
  phase = sc@meta.data$Phase,
  experiment = sapply(sc@cell.names, get.pop.name),
  stringsAsFactors=F
)
rownames(cells.phases) <- sc@cell.names
```

### Convert `cells.phases` Into A Phase x Experiment Matrix

```{r}
phase.count <- ddply(cells.phases, .(cells.phases$phase, cells.phases$experiment), nrow)
names(phase.count) <- c("phase", "experiment", "count")
phase.count.mat <- acast(phase.count, phase~experiment, value.var="count")
phase.count.mat <- phase.count.mat/colSums(phase.count.mat)[col(phase.count.mat)]
```

### Build Heatmap

```{r}
ph <- pheatmap(phase.count.mat, cluster_rows=F, cluster_cols=T, 
               show_rowname=T, show_colnames=T, silent=F,
               fontsize=20, border_color="black")
```

### Load 10X Clusters

```{r results="hide"}
clusters <- read.csv("../deep_5uM/graphclust/clusters.csv")
```

### Compile Experiment And Cluster

```{r}
exps.clusters <- data.frame(
  experiment = sapply(sc@cell.names, get.pop.name),
  cluster = clusters$Cluster,
  stringsAsFactors=F
)
rownames(exps.clusters) <- sc@cell.names
```

### Build Experiment by Cluster Matrix

```{r}
clust.count <- ddply(exps.clusters, .(exps.clusters$cluster, exps.clusters$experiment), nrow)
names(clust.count) <- c("cluster", "experiment", "count")
clust.count.mat <- acast(clust.count, cluster~experiment, value.var="count", fill=0)
clust.count.mat <- clust.count.mat/colSums(clust.count.mat)[col(clust.count.mat)]
```

### Build Heatmap

```{r}
ph <- pheatmap(clust.count.mat, cluster_rows=F, cluster_cols=T, 
                   show_rowname=T, show_colnames=T, silent=F,
                fontsize=20, border_color="black")
```

### Compile Cluster and Phase

```{r}
exps.clusters <- data.frame(
  phase = sc@meta.data$Phase,
  cluster = clusters$Cluster,
  stringsAsFactors=F
)
rownames(exps.clusters) <- sc@cell.names
```

### Build Phase by Cluster Matrix

```{r}
clust.count <- ddply(exps.clusters, .(exps.clusters$phase, exps.clusters$cluster), nrow)
names(clust.count) <- c("phase", "cluster", "count")
clust.count.mat <- acast(clust.count, phase~cluster, value.var="count", fill=0)
clust.count.mat <- clust.count.mat/colSums(clust.count.mat)[col(clust.count.mat)]
```

### Build Heatmap

```{r}
ph <- pheatmap(clust.count.mat, cluster_rows=F, cluster_cols=T, 
                   show_rowname=T, show_colnames=T, silent=F,
               fontsize=20, border_color="black")
```
