---
title: "deep_5uM 10X Metacluster GSEA"
output: html_notebook
---

This performs a similar analysis to [deep_5uM_cca_cluster_comp.Rmd](https://github.com/alex-wenzel/cptres-r/blob/master/deep_5uM_cca_cluster_comp.Rmd)
except without `Seurat` cell cycle regression or clustering. Membership in sensitive or resistant groups
is determined by `10X` clustering only (clusters 1-3 being sensitive, all others being resistant). 

### Libraries

```{r}
library(grid)
library(plyr)
library(dplyr)
library(GSA)
library(liger)
library(matrixStats)
library(parallel)
library(pheatmap)
library(Seurat)
library(stringr)
library(reshape2)
library(fgsea)
library(biomaRt)
```

### Load Seurat

Load data ***without*** applying cell cycle regression.

```{r}
scdata <- Read10X(data.dir="../deep_5uM/")
sc <- CreateSeuratObject(raw.data=scdata, min.cells=3, min.genes=3, project="deep_5uM")
sc <- NormalizeData(object=sc, normalization.method="LogNormalize", scale.factor=10000)
sc <- ScaleData(object=sc)
```

### Map Experiment Names

```{r}
exp.names <- c("S02", "S03", "caov3", "parent", "R06_5uM", "R14_5uM",
               "R16_5uM", "R18_5uM")
names(exp.names) <- 1:8
get.pop.name <- function(bc) {
  exp.names[as.numeric(strsplit(bc, "-")[[1]][2])]
}
```

### Compile Cell Metadata

Get the experiment name and `10X` graph cluster membership for each cell.

```{r}
cells.metadata = data.frame(
  experiment = sapply(sc@cell.names, get.pop.name),
  cluster = as.numeric(read.csv("../deep_5uM/graphclust/clusters.csv")$Cluster),
  row.names = sc@cell.names,
  stringsAsFactors = F
)
```

### Meta Cluster Assignment Function

```{r}
get.meta.cluster <- function(experiment, cluster) {
  if (cluster <= 3) {
    paste(experiment, "_sen", sep="")
  } else {
    paste(experiment, "_res", sep="")
  }
}
```

### Assign Meta Clusters

```{r}
cells.metadata$metacluster <- mapply(get.meta.cluster, cells.metadata$experiment,
                                     cells.metadata$cluster)
sc@ident <- as.factor(cells.metadata$metacluster)
attributes(sc@ident)$names <- sc@cell.names
```

### Find DEG Markers

```{r}
sc.markers <- FindAllMarkers(object=sc, min.pct=0, thresh.use=0)
```

### Top 10 Genes in Each Cluster

```{r fig.height=15, fig.width=15}
top.10.genes <- sc.markers %>% group_by(cluster) %>% top_n(10, avg_logFC)
```

### Heatmap of Untreated Cells

```{r}
untreated.markers <- FindMarkers(object=sc, ident.1=c("caov3_sen", "parent_sen", "S02_sen", "S03_sen"),
                                 ident.2=c("caov3_res", "parent_res", "S02_res", "S03_res"))
```

### Untreated Cells Heatmap

```{r fig.width=15}
untreated.cell.names = rownames(cells.metadata[cells.metadata$experiment %in% c("caov3", "parent", "S02", "S03"),])
DoHeatmap(object=sc, genes.use=rownames(untreated.markers)[1:50], slim.col.label=T,
          remove.key=T, cells.use=untreated.cell.names)
```

### Load Gene Sets

```{r results="hide"}
hallmarks.full <- GSA.read.gmt("../msigdb/h.all.v6.1.symbols.gmt")
hallmarks <- hallmarks.full$genesets
names(hallmarks) <- hallmarks.full$geneset.names

reactome.full <- GSA.read.gmt("../msigdb/c2.cp.reactome.v6.1.symbols.gmt")
reactome <- reactome.full$genesets
names(reactome) <- reactome.full$geneset.names
```

### GSEA Wrapper

```{r}
run.fgsea <- function(gene.set, pcut, markers) {
  cluster.stats <- markers$avg_logFC
  names(cluster.stats) <- rownames(markers)
  res <- fgsea(pathways=gene.set, stats=cluster.stats, nperm=10000, minSize=10)
  res <- res[res$padj<pcut,]
  return(res)
}
```

### Untreated Cells GSEA

```{r}
hmrks <- run.fgsea(hallmarks, 0.05, untreated.markers)
react <- run.fgsea(reactome, 0.05, untreated.markers)
```

### Add Entrez IDS

Add Entrez Gene IDs to `untreated.markers` for input into `RGES`

```{r}
ensembl <- useMart("ensembl", dataset="hsapiens_gene_ensembl")
query.values <- rownames(untreated.markers)
query.filters=c("hgnc_symbol")
query.attributes=c("hgnc_symbol", "entrezgene")
query.res <- getBM(attributes=query.attributes, filters=query.filters, values=query.values,
                   mart=ensembl, uniqueRows=F)
dupRows <- union(which(duplicated(query.res[,1])), which(duplicated(query.res[,2])))
entrezIds <- query.res[-dupRows]
entrezIds <- entrezIds[!duplicated(entrezIds$hgnc_symbol),]
rownames(entrezIds) <- entrezIds$hgnc_symbol

map.entrez <- function(symbol){entrezIds[symbol,][2]}

untreated.markers$entrezgene <- sapply(rownames(untreated.markers), map.entrez)
untreated.markers$entrezgene <- unlist(untreated.markers$entrezgene)
write.table(untreated.markers, "../RGES/deep_untreated_markers.tsv", sep='\t', quote=F, row.names=F)
```

