---
title: "deep_5uM Cell Cycle Assignment Cluster Comparison"
output: html_notebook
---

This notebook performs a similar analysis to [`deep_5uM Cell Cycle Assignment`](https://github.com/alex-wenzel/cptres-r/blob/master/deep_5uM_cell_cycle_assignment.Rmd) but creates
a more comprehensive visualization by building a heatmap that involves meta clustering from both `Seurat` and `10X` graph
based clustering. Each experiment will take up four rows in the heatmap, one each for `Seurat` sensitive, `Seurat` resistant,
`10X` sensitive and `10X` resistant clustering. In both `Seurat` and `10X`, clusters 1-3 are sensitive and all others
are resistant. `Seurat` clustering is done with cell cycle regression.

### Libraries

```{r results="hide"}
library(grid)
library(plyr)
library(dplyr)
library(GSA)
library(liger)
library(matrixStats)
library(parallel)
library(pheatmap)
library(Seurat)
library(stringr)
library(reshape2)
library(fgsea)
```

### Load Seurat

Load data, normalize, scale, apply cell cycle regression

```{r}
scdata <- Read10X(data.dir="../deep_5uM/")
sc <- CreateSeuratObject(raw.data=scdata, min.cells=3, min.genes=3, project="deep_5uM")
sc <- NormalizeData(object=sc, normalization.method="LogNormalize", scale.factor=10000)
sc <- ScaleData(object=sc)
cc.genes <- readLines(con="../satija_cell_cycle/regev_lab_cell_cycle_genes.txt")
s.genes <- cc.genes[1:43]
g2m.genes <- cc.genes[44:97]
sc <- CellCycleScoring(object=sc, s.genes=s.genes, g2m.genes=g2m.genes, set.ident=T)
sc <- ScaleData(object=sc, vars.to.regress=c("S.Score", "G2M.Score"))
```


### Run PCA

```{r}
sc <- FindVariableGenes(object=sc, mean.function=ExpMean, 
                        dispersion.function=LogVMR, x.low.cutoff=0.0125,
                        x.high.cutoff=3, y.cutoff=0.5, do.plot=F)
sc <- RunPCA(object=sc, pc.genes=sc@var.genes, do.print=F)
```

### Find Optimal Dimension Count For Clusters

```{r}
PCElbowPlot(object=sc)
```


### Find PCA-based clusters

```{r}
sc <- FindClusters(object=sc, reduction.type="pca", dims.use=1:10,
                   resolution=0.6, print.output=0, save.SNN=T)
```


### Map Experiment Names

```{r}
exp.names <- c("S02", "S03", "caov3", "parent", "R06_5uM", "R14_5uM",
               "R16_5uM", "R18_5uM")
names(exp.names) <- 1:8
get.pop.name <- function(bc) {
  exp.names[as.numeric(strsplit(bc, "-")[[1]][2])]
}
```

### Visualize Seurat Clusters

Visually identify sensitive and resistant clusters

```{r}
exp.names <- c("S02", "S03", "caov3", "parent", "R06_5uM", "R14_5uM",
               "R16_5uM", "R18_5uM")
names(exp.names) <- 1:8
get.pop.name <- function(bc) {
  exp.names[as.numeric(strsplit(bc, "-")[[1]][2])]
}
cells.clusters <- data.frame(
  cluster = sc@ident,
  experiment = sapply(sc@cell.names, get.pop.name),
  stringsAsFactors=F
)
rownames(cells.clusters) <- sc@cell.names
clusters.count <- ddply(cells.clusters, .(cells.clusters$cluster, cells.clusters$experiment), nrow)
names(clusters.count) <- c("cluster", "experiment", "count")
clusters.count.mat <- acast(clusters.count, cluster~experiment, value.var="count", fill=0)
clusters.count.mat <- clusters.count.mat/colSums(clusters.count.mat)[col(clusters.count.mat)]
ph <- pheatmap(clusters.count.mat, cluster_rows=F, cluster_cols=T, 
               show_rowname=T, show_colnames=T, silent=F,
               fontsize=20, border_color="black")
```

```{r}
seurat.sensitive <- c(1, 3, 5, 7, 8)
seurat.resistant <- c(0, 2, 4, 6)
```


### Compile metadata

Build a data frame in which each row is a cell labeled with its experiment and membership in either `seurat_sensitive`,
`seurat_resistant`, `10x_sensitive` and `10x_resistant`. 

```{r}
sc.metacluster <- data.frame(
  experiment = sapply(sc@cell.names, get.pop.name),
  row.names=sc@cell.names,
  orig.cluster=as.numeric(read.csv("../deep_5uM/graphclust/clusters.csv")$Cluster),
  seurat.cluster=as.numeric(sc@ident),
  phase=sc@meta.data$Phase,
  stringsAsFactors=F
)

get.meta.cluster <- function(r) {
  seurat <- as.numeric(r[3])
  original <- as.numeric(r[2])
  if (seurat <= 3 && original %in% seurat.sensitive) {
    "Srt-S_10x-S"
  } else if (seurat <= 3 && original %in% seurat.resistant) {
    "Srt-S_10x-R"
  } else if (seurat > 3 && original %in% seurat.sensitive) {
    "Srt-R_10x-S"
  } else {
    "Srt-R_10x-R"
  }
}

sc.metacluster$meta.cluster <- apply(sc.metacluster, 1, get.meta.cluster)
```

### Build Cell Phase Matrix

```{r}
phase.count <- ddply(sc.metacluster, .(sc.metacluster$phase, sc.metacluster$meta.cluster), nrow)
names(phase.count) <- c("phase", "meta.cluster", "count")
phase.count.mat <- acast(phase.count, phase~meta.cluster, value.var="count")
phase.count.mat
phase.count.mat <- phase.count.mat/colSums(phase.count.mat)[col(phase.count.mat)]
```

### Build Heatmap

```{r}
ph <- pheatmap(phase.count.mat, cluster_rows=F, cluster_cols=F, 
               show_rowname=T, show_colnames=T, silent=F,
               fontsize=20, border_color="black")
```

