---
title: "deep_5uM CAOV3 Sensitive/Resistant GSEA"
output: html_notebook
---

This notebook classifies the CAOV3 cells into sensitive (graphclust 1-3) and resistant
(graphclust 4-9) states and performs GSEA based on the `Seurat`-identified variable
genes between these clusters.

### Libraries

```{r results="hide"}
library(grid)
library(plyr)
library(dplyr)
library(GSA)
library(liger)
library(matrixStats)
library(parallel)
library(pheatmap)
library(Seurat)
library(stringr)
library(reshape2)
library(fgsea)
```

### Load Seurat Data

Load, normalize, regress cell cycle signature

```{r results="hide"}
scdata <- Read10X(data.dir="../deep_5uM/")
sc <- CreateSeuratObject(raw.data=scdata, min.cells=3, min.genes=3, project="deep_5uM")
sc <- NormalizeData(object=sc, normalization.method="LogNormalize", scale.factor=10000)
sc <- ScaleData(object=sc)
cc.genes <- readLines(con="../satija_cell_cycle/regev_lab_cell_cycle_genes.txt")
s.genes <- cc.genes[1:43]
g2m.genes <- cc.genes[44:97]
sc <- CellCycleScoring(object=sc, s.genes=s.genes, g2m.genes=g2m.genes, set.ident=T)
sc <- ScaleData(object=sc, vars.to.regress=c("S.Score", "G2M.Score"))
```

### Assign Experiment Name

```{r}
exp.names <- c("S02", "S03", "caov3", "parent", "R06_5uM", "R14_5uM",
               "R16_5uM", "R18_5uM")
names(exp.names) <- 1:8
get.pop.name <- function(bc) {
  exp.names[as.numeric(strsplit(bc, "-")[[1]][2])]
}

cells.exp <- data.frame(
  experiment = sapply(sc@cell.names, get.pop.name),
  cluster = read.csv("../deep_5uM/graphclust/clusters.csv")$Cluster,
  stringsAsFactors = F
)
rownames(cells.exp) <- sc@cell.names
```

### Assign Sensitive or Resistant

```{r}
get.state <- function(experiment, cluster) {
  if (experiment == "caov3")
  {
    if (cluster <= 3) {
      "sensitive"
    } else {
      "resistant"
    }
  } else {
    "irrelevant"
  }
}

cells.exp$state <- mapply(get.state, cells.exp$experiment, cells.exp$cluster)
new.ident <- as.factor(cells.exp$state)
attributes(new.ident)$names <- sc@cell.names
sc@ident <- new.ident
```

### Find Differentially Expressed Genes

```{r}
resistant.markers <- FindMarkers(object=sc, ident.1="sensitive", ident.2="resistant",
                                 min.pct=0, thresh.use=0)
resistant.markers$gene <- rownames(resistant.markers)
```

### Sensitive/Resistant Markers Heatmap

```{r fig.height=9, fig.width=13}
top.25.genes <- resistant.markers %>% top_n(25, avg_logFC)
low.25.genes <- resistant.markers %>% top_n(25, -avg_logFC)
DoHeatmap(object=sc, genes.use=append(top.50.genes$gene, low.25.genes$gene), 
          slim.col.label=T, remove.key=T, use.scaled=T,
          cells.use=rownames(cells.exp[cells.exp$experiment=="caov3",]))
```

### Load Gene Sets

```{r results="hide"}
hallmarks.full <- GSA.read.gmt("../msigdb/h.all.v6.1.symbols.gmt")
hallmarks <- hallmarks.full$genesets
names(hallmarks) <- hallmarks.full$geneset.names

reactome.full <- GSA.read.gmt("../msigdb/c2.cp.reactome.v6.1.symbols.gmt")
reactome <- reactome.full$genesets
names(reactome) <- reactome.full$geneset.names
```

### GSEA Wrapper

```{r}
run.fgsea <- function(cluster.name, gene.set) {
  cluster.markers <- sc.markers[sc.markers$cluster==cluster.name,]
  cluster.stats <- cluster.markers$avg_logFC
  names(cluster.stats) <- cluster.markers$gene
  res <- fgsea(pathways=gene.set, stats=cluster.stats, nperm=10000, minSize=10)
  top.pathways.up <- res[ES>0,][head(order(pval), n=10), pathway]
  top.pathways.dn <- res[ES<0,][head(order(pval), n=10), pathway]
  top.pathways <- c(top.pathways.up, rev(top.pathways.dn))
  plotGseaTable(gene.set[top.pathways], cluster.stats, res, gseaParam=0.5)
  return(res)
}
```

### GSEA

```{r fig.width=20, fig.height=10}
resistant.stats <- resistant.markers$avg_logFC
names(resistant.stats) <- resistant.markers$gene

hmrks.res <- fgsea(pathways=hallmarks, stats=resistant.stats, nperm=10000, minSize=10)
top.pathways.up <- hmrks.res[ES>0,][head(order(pval), n=10), pathway]
top.pathways.dn <- hmrks.res[ES<0,][head(order(pval), n=10), pathway]
top.pathways <- c(top.pathways.up, rev(top.pathways.dn))
plotGseaTable(hallmarks[top.pathways], resistant.stats, hmrks.res, gseaParam=0.5)

react.res <- fgsea(pathways=reactome, stats=resistant.stats, nperm=10000, minSize=10)
top.pathways.up <- react.res[ES>0,][head(order(pval), n=10), pathway]
top.pathways.dn <- react.res[ES<0,][head(order(pval), n=10), pathway]
top.pathways <- c(top.pathways.up, rev(top.pathways.dn))
plotGseaTable(reactome[top.pathways], resistant.stats, react.res, gseaParam=0.5)
```

